getwd()
setwd("C:/Users/hihuj/Desktop/miningOLD")
dataset = read.csv('hobbyperdectionOLD.csv')
names(dataset)

max(dataset$Time_art)
quantile(dataset$Sepal.Length, c(0.1, 0.3, 0.65))

OutAge = outlier(dataset$Time_sprt, logical =TRUE)
sum(OutAge)
Find_outlier = which(OutAge ==TRUE, arr.ind = TRUE)
OutAge
Find_outlier

boxplot(dataset$Grasp_pow)
```{r}
boxplot(Time_art ~ Predicted.Hobby, data = dataset)

```


with(dataset, plot(Grasp_pow, Time_sprt, col = Predicted.Hobby, pch = as.numeric(Predicted.Hobby)))

boxplot(Time_sprt ~ Predicted.Hobby, data = dataset)
summary(dataset$Grasp_pow)
boxplot.stats(dataset$Grasp_pow)$out
boxplot(dataset$Grasp_pow)
#outlier selotion
boxplot(dataset$Grasp_pow, range = 10)

summary(dataset$Time_art)
boxplot(dataset$Time_art)
boxplot.stats(dataset$Time_art)$out
max(dataset$Time_art)


summary(dataset$Time_sprt)
boxplot.stats(dataset$Time_sprt)$out
boxplot(dataset$Time_sprt)

str(dataset)
attributes(dataset)

hist(dataset$Grasp_pow) #done

```{r}
dataset$Time_sprt %>% density() %>% plot(main='Density of Time_sprt')

```

```{r}
dataset2 <- dataset %>% sample_n(50)
dataset2$Predicted.Hobby %>% table() %>% pie() # plot pie chart without percentages
# add percentages
tab <- dataset2$Predicted.Hobby %>% table()
precentages <- tab %>% prop.table() %>% round(3) * 100 
txt <- paste0(names(tab), '\n', precentages, '%') # text on chart
pie(tab, labels=txt) # plot pie chart
```
dataset2 <- dataset %>% sample_n(50)
dataset2$Predicted.Hobby %>% table() %>% pie() # plot pie chart without percentages
# add percentages
tab <- dataset2$Predicted.Hobby %>% table()
precentages <- tab %>% prop.table() %>% round(3) * 100 
txt <- paste0(names(tab), '\n', precentages, '%') # text on chart
pie(tab, labels=txt) # plot pie chart
------------------------------------------------------------------------------------------
dataset2 <- dataset %>% sample_n(50)
dataset2$Won_arts %>% table() %>% pie() # plot pie chart without percentages
# add percentages
tab <- dataset2$Won_arts %>% table()
precentages <- tab %>% prop.table() %>% round(3) * 100 
txt <- paste0(names(tab), '\n', precentages, '%') # text on chart
pie(tab, labels=txt) # plot pie chart
------------------------------------------------------------------------------


#Bar Chart
dataset2$Predicted.Hobby %>% table() %>% barplot() #plot bar chart
# add colors and percentages
bb <- dataset2$Predicted.Hobby %>% table() %>% barplot(axisnames=F, main='Predicted.Hobby', ylab='Frequency',col=c('pink', 'lightblue', 'lightgreen'))
text(bb, tab/2.5, labels=txt, cex=1)

-----------------------------------------------------------------------------
with(dataset, plot(Grasp_pow, Time_sprt, col = Species, pch = as.numeric(Predicted.Hobby)))
------------------------------------------------------------------------------
pairs(dataset)



